### 2015-05-17 Pros_KI/Pros_speechprocessing_v1.tex
added bird quote

\section{Was ist natürliche Sprache?}
\label{sec:def_lang}
\begin{itemize}
    \item Zitat von Bird
    \item Analyse des Zitates mit Interpretation
    \item Auflistung und minimale Erläuterung der sechs zu erarbeitenden Eigenschaften
\end{itemize}

>>>>

\section{Was ist natürliche Sprache?}
\label{sec:def_lang}
\textit{„By "natural language" we mean a language that is used for everyday communication by humans; languages such as English, Hindi, or Portuguese.
        In contrast to artificial languages such as programming languages and mathematical notations, natural languages have evolved as they pass from generation to generation.
        and are hard to pin down with explicit rules.“}
\begin{flushright}
    \textit{-~~Steven Bird et.al., 2009}
\end{flushright}
\begin{itemize}
    \item Analyse des Zitates mit Interpretation
    \item Auflistung und minimale Erläuterung der sechs zu erarbeitenden Eigenschaften
\end{itemize}
